Recursive algorithms, branching coefficients and applications

### 2010-09-12 AffineLieAlgebras/InformalNotes/article.tex
New definitions are introduced, the proof is rewritten.

\newtheorem{statement}{Statement}
\newtheorem{mynote}{Note}[section]
%\theoremstyle{definition} \newtheorem{Def}{Definition}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}

@@

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras integrable highest weight modules are studied. The decomposition algorithm based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive subalgebra. We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original ones. Possible applications of subtracted fans in CFT models are considered.
\end{abstract}
\submitto{\JPA}
%\maketitle

@@

Our aim is to demonstrate that despite the zeros arriving in the Weyl denominator $R$
(when it is projected to $P_{\mathfrak{a}}$) the injection fan technique \cite{ilyin812pbc} can be properly modified.
The result is the generalized recurrent relation for anomalous branching
coefficients (\ref{eq:21}):
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
  {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
  \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right).
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra fixed by those roots of $\mathfrak{g}$ that are
orthogonal to $P_{\mathfrak{a}}$, $W_{\bot}$ is the corresponding Weyl group,
$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
is the multiplicity of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the relation (\ref{eq:1}).

\subsection{Proof of the recurrent relation}
\label{sec:proof}

Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
\begin{equation*}
%  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
\end{equation*}
The Weyl-Kac character formula leads to
the relation
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
\end{equation}

Consider the positive roots $\alpha\in \Delta$ orthogonal to $P_{\mathfrak{a}}$.
Denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.
Notice that if $\Delta^{+}_{\bot}\neq \emptyset$ the corresponding Weyl reflections
generate a subgroup $W_{\bot}$ of the group $W$. Consider the roots $\alpha,\;
\beta\in \Delta^{+}_{\bot}$ and the corresponding reflections
$\omega_{\alpha},\; \omega_{\beta}\in W_{\bot}$.  Since the roots in $\Delta_{\mathfrak{a}}$
are invariant with respect to $\omega_{\alpha}, \; \omega_{\beta}$
and $\omega_{\gamma}=\omega_{\alpha}\cdot \omega_{\beta}$
the subgroup $W_{\bot}$ preserves the roots in $\Delta_{\mathfrak{a}}$.
The subsystem $\Delta_{\bot}$
can be considered as the root system of a subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.

Now we are to find out when the subset $\Delta^{+}_{\bot}$ is nonempty
with the nontrivial subgroup $W_{\bot}$ and the subalgebra $\mathfrak{a}_{\bot}$.

If $\mathfrak{a}$ is a maximal regular subalgebra of $\mathfrak{g}$ then $r_{\mathfrak{a}}=r$ and
 $\Delta^{+}_{\bot}$ is empty.
On the other hand
nonmaximal regular embedding of $\mathfrak{a}$ into $\mathfrak{g}$ can be obtained
through the chain of maximal embeddings
$\mathfrak{a}\subset \mathfrak{p}_1\subset \mathfrak{p}_2\subset\dots \subset \mathfrak{g}$.
The maximal regular embeddings can be described by the elimination of one or two roots
from the extended Dynkin diagram of the algebra. When the process gives us
nonconnected diagrams we immediately fix the roots orthogonal to $P_{\mathfrak{a}}$.
The complete classification of the regular subalgebras for affine Lie algebras can be
found in the recent paper \cite{1751-8121-41-36-365204}.

For a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$
and $\mathfrak{g}$ are simple the sufficient condition for $\Delta^{+}_{\bot}$ to be
nontrivial can be formulated as follows:
if the Dynkin diagram of $\mathfrak{g}$ contains the disconnected
subdiagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
then the subset $\Delta_{\bot}$ is not empty,
subalgebra $\mathfrak{a}_{\bot}$ is nontrivial and
$\left\{\mathfrak{\bar{a}}_j\right\}$ are the subalgebras of $\mathfrak{a}_{\bot}$.

Notice that when we study the regular embedding obtained by dropping the nodes
of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the
subalgebra $\mathfrak{a}$ is one of the connected components,
the subalgebra $\mathfrak{a}_{\bot}$ may be larger than the algebra
generated by the remaining connected components of the diagram.
Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
In this case by eliminating
the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$
(the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$
must not form a direct sum in $\mathfrak{g}$.
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both
algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a
subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with
the remaining nodes of the diagram of $\mathfrak{g}$. The result is the diagram of
the algebra $\bar{\mathfrak{a}}$ with $\mathrm{rank}(\bar{\mathfrak{a}}) =
\mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that
$\bar{\mathfrak{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether
$\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\bar{\mathfrak{a}}$
but the linear combinations of them. The answer is positive  when the set of angles
between the roots of $\bar{\mathfrak{a}}$ does not contain all the angles between
the roots of $\mathfrak{a}$.
Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional
roots of $\mathfrak{a}_{\bot}$.
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ &
  Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps} \\
  \hline
  $B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps} \\
  \hline
  $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps} \\
  \hline
  $D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}
If $\mathfrak{a}=B_{r_{\mathfrak{a}}}$  we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\;
1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
This is the only case where the simple roots of $\mathfrak{a}_{\bot}$ can not be
obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.

Using the existing classification of maximal special subalgebras in classical Lie algebras
\cite{dynkin1952semisimple} we have the following pairs of the orthogonal
subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation*}
%  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}.\\
  \end{array}
\end{equation*}

Now consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
can be written as
\begin{equation*}
%  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}=
  \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
  e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
  {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
\end{equation*}
Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$
is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$
with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

Using this property we can consider the restriction
$ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
Multiply the equation (\ref{eq:4}) by the element
\begin{equation*}
%  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}
  (1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation*}
and take into account that the projection commutes with the multiplication:
\begin{eqnarray*}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
\end{eqnarray*}
Similarly to the transformation proposed in \cite{ilyin812pbc} we introduce the anomalous branching coefficients $k_{\lambda}$,
\begin{equation*}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation*}
and simplify the first factor,
\begin{eqnarray*}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
\end{eqnarray*}

>>>>

\newtheorem{statement}{Statement}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{corollary}{Corollary}[theorem]
\theoremstyle{definition}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}

@@

\begin{abstract}
  Recurrent relations for branching coefficients in affine Lie algebras integrable highest weight modules are studied. The decomposition algorithm based on the injection fan technique is adopted to the situation where the Weyl denominator becomes singular with respect to a reductive subalgebra. We study some modifications of the injection fan technique and demonstrate that it is possible to define the "subtracted fans" that play the role similar to the original ones. Possible applications of subtracted fans in CFT models are considered.
\end{abstract}
\ams{17B67, 17B10}
\submitto{\JPA}
%\maketitle

@@

We consider an injection of affine Lie algebras $\frak{a}\longrightarrow \frak{g%
}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$.
In this section we deduce the general recurrent relation (\ref{eq:1}) for the anomalous branching coefficients (\ref{eq:21}). This relation is then used to formulate the practical computational algorithm (Subsection \ref{sec:algorithm}).
In the earlier paper \cite{ilyin812pbc} the following limited setup was considered: $\mathfrak{a}$ was required to be the maximal subalgebra of $\mathfrak{g}$ so that no zeros arrive in the Weyl denominator $R$. Here we raise this limitation and study the general case $\mathfrak{a}\subset\mathfrak{g}$.

\subsection{Some definitions}
\label{sec:some-definitions}

We need to introduce several additional definitions and state some technical results to formulate and prove the recurrent relation (\ref{eq:1}).

\begin{definition}
  Denote by $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\mathfrak{a}} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$.
\end{definition}

\begin{definition}
  Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
\end{definition}
\begin{mynote}
  The subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\mathfrak{a}}$.
\end{mynote}
\begin{definition}
  The subsystem $\Delta_{\bot}=\Delta^{+}_{\bot}\cup \left(-\delta^{+}_{\bot}\right)$ determines the subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
\end{definition}

We need to know when the subset $\Delta^{+}_{\bot}$ is non-empty and $W_{\bot},\mathfrak{a}_{\bot}$ are non-trivial. So we state several simple lemmas.

For the simple finite-dimensional Lie algebras $\ao,\go$ all the regular embeddings can be obtained by the successive elimination of the nodes in the extended Dynkin diagram of $\go$. This leads to the lemma
\begin{lemma}
  For the regular embedding $\ao\subset \go$ 
  \renewcommand{\theenumi}{\alph{enumi}}
  \begin{enumerate}
  \item $\Delta^{+}_{\bot}=\emptyset$ if $\ao$ is maximal
  \item If the extended Dynkin diagram of $\go$ contains the disconnected subdiagrams of $\ao$ and some subalgebras $\left\{\co{\mathfrak{a}_j}\right\}$ then $\Delta^{+}_{\bot}\neq \emptyset$ and $\co{\mathfrak{a}_j}\subset \mathfrak{a}_{\bot}$.
  \end{enumerate}
\end{lemma}
\begin{mynote}
  The complete classification of the regular subalgebras for affine Lie algebras can be
  found in the recent paper \cite{1751-8121-41-36-365204}.
\end{mynote}
\begin{mynote}
  $\mathfrak{a}_{\bot}$ may be larger than the algebra $\bigoplus_j \co{\mathfrak{a}_j}$.
\end{mynote}
Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
In this case by eliminating
the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$
(the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$
must not form a direct sum in $\mathfrak{g}$.
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both
algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a
subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with
the remaining nodes of the diagram of $\mathfrak{g}$. The result is the diagram of
the algebra $\bar{\mathfrak{a}}$ with $\mathrm{rank}(\bar{\mathfrak{a}}) =
\mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that
$\bar{\mathfrak{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether
$\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\bar{\mathfrak{a}}$
but the linear combinations of them. The answer is positive  when the set of angles
between the roots of $\bar{\mathfrak{a}}$ does not contain all the angles between
the roots of $\mathfrak{a}$.
Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional
roots of $\mathfrak{a}_{\bot}$.
Case-by-case analysis illustrated by the table \ref{tab:diagrams} leads us to the following lemma.

\begin{table}[h!tb]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ &
  Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps} \\
  \hline
  $B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps} \\
  \hline
  $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps} \\
  \hline
  $D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}

\begin{lemma}
  \renewcommand{\theenumi}{\alph{enumi}}
  \begin{enumerate}
  \item If $\go,\ao\neq B_r$ the Dynkin diagram of $\mathfrak{a}_{\bot}$ is obtained from the extended Dynkin diagram of $\go$ by dropping the subdiagram of $\ao$ and the adjacent nodes
  \item If $\go=B_r$ and $\ao=B_{r_{\mathfrak{a}}}$ then $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
  \end{enumerate}
\end{lemma}
The complete classification of maximal special subalgebras in classical Lie algebras
\cite{dynkin1952semisimple} allows us to formulate
\begin{lemma}
  For the special embeddings there exist the following set of pairs of orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$:
\begin{equation*}
%  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}.\\
  \end{array}
\end{equation*}
\end{lemma}
We are almost ready to state and prove the recurrent relation for the anomalous branching coefficients.
\begin{definition}
  \label{fan-definition}
  For affine $\mathfrak{a}\subset\mathfrak{g}$ expand the product
  \begin{equation*}
    \label{eq:6}
    \prod_{\alpha\in \Delta^{+}\setminus\Delta^{+}_{\bot}}
    \left(1-e^{-\pi_{\mathfrak{a}}\alpha}\right)^{
        \mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}\alpha)}=
      -\sum_{\gamma\in P_{\mathfrak{a}}}e^{-\gamma}
  \end{equation*}
  Denote by $\Phi_{\mathfrak{a}\subset\mathfrak{g}}\subset P_{\mathfrak{a}}$ the carrier of the coefficient function $s(\gamma)$. 
  \begin{equation*}
    \label{eq:37}
    \Phi_{\mathfrak{a}\subset\mathfrak{g}}=\left\{\gamma\in P_{\mathfrak{a}}|s(\gamma)\neq 0\right\}
  \end{equation*}

  The ordering of roots in $\co{\Delta_{\mathfrak{a}}}$ induce the natural ordering on the weights of $\mathfrak{a}$. Denote by $\gamma_0$ the lowest vector of $    \Phi_{\mathfrak{a}\subset\mathfrak{g}}$ according to this ordering. 
  The set 
  \begin{equation}
    \Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
        \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
    \label{fan-defined}
  \end{equation}
  is called the {\it injection fan}.
\end{definition}

\subsection{Proof of the recurrent relation}
\label{sec:proof}
\begin{theorem}
  For the anomalous branching coefficients (\ref{eq:21}) holds the recurrent relation
  \begin{equation}
    \label{eq:1}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}
  \begin{proof}
    Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
    projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
    \begin{equation*}
      % \label{eq:3}
      L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
        }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
      \Longrightarrow\quad
      \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
    \end{equation*}
    The Weyl-Kac character formula leads to
    the relation
    \begin{equation}
      \label{eq:4}
      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
        {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
        e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
      {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
    \end{equation}

    Consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
    its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
    with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
    can be written as
    \begin{equation*}
      % \label{eq:41}
      ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}=
      \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
        e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
      {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
    \end{equation*}
    Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$
    is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$
    with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
    since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

    Using this property we can consider the restriction
    $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
    that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
    Multiply the equation (\ref{eq:4}) by the element
    \begin{equation*}
      % \label{eq:5}
      \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}
        (1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
    \end{equation*}
    and take into account that the projection commutes with the multiplication:
    \begin{eqnarray*}
      \label{eq:7}
      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
      \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
    \end{eqnarray*}
    Rewriting this relation in terms of the anomalous branching coefficients (\ref{eq:21}) and simplifying the first factor we get
    \begin{eqnarray*}
      \label{eq:12}
      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
      \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
      \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
    \end{eqnarray*}
